A studyforrest extension, an annotation of words and phonemes in the German dubbed movie ``Forrest Gump'' and its audio-description

### 2020-04-15 paper/main.tex
Sort tables where they belong in the text

\begin{table*}[t]
\caption{Overview of the speech annotation's content for the whole stimulus and it's individual segments. The label ``Sentences''' comprises complete grammatical sentences (i.e. having a subject and a predicate, and additionally marked with a full stop in the annotation). The  ``Sentences'' also comprises exlamations or non-speech vocalizations in quick succession (e.g. ``ha, ha, ha'') or in isolation (e.g. ``ha'', at time points when speakers rapidly switch). The label ``Words'' comprises every single word or non-speech vocalization (N=\aPosNonspeechAll) in isolation.}
\label{tab:overview}
\begin{tabular}{llllllllll}
\toprule
\textbf{label} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8}\\
\midrule
sentences  & \aSentencesAll & \aSentencesI & \aSentencesII & \aSentencesIII & \aSentencesIV & \aSentencesV & \aSentencesVI & \aSentencesVII & \aSentencesVIII \tabularnewline
words  & \aWordsAll & \aWordsI & \aWordsII & \aWordsIII & \aWordsIV & \aWordsV & \aWordsVI & \aWordsVII & \aWordsVIII \tabularnewline
phonemes  & \aPhonesAll & \aPhonesI & \aPhonesII & \aPhonesIII & \aPhonesIV & \aPhonesV & \aPhonesVI & \aPhonesVII & \aPhonesVIII \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

% bei ein paar Namen bin ich ggf. von Labs abgewichen (genauer identifiziert, ggf. kleine Fehler korrigiert. Ist dann aber nur bei Personen, die 1-2x mit 1-2 Sätzen auftauchen.
\begin{table*}[t]
\caption{Sentences spoken by the ten most often occurring speakers sorted alphabetically. The narrator only occurrs in the audio-description of the movie. Shown names are identical to the names used in \citep{labs2015portrayed}. Overall 97 persons were identified.}
\label{tab:speakers}
\begin{tabular}{llllllllll}
\toprule
\textbf{name} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8}\\
\midrule
Bubba  & \aBubbaAll & \aBubbaI & \aBubbaII & \aBubbaIII & \aBubbaIV & \aBubbaV & \aBubbaVI & \aBubbaVII & \aBubbaVIII \tabularnewline
Forrest  & \aForrestAll & \aForrestI & \aForrestII & \aForrestIII & \aForrestIV & \aForrestV & \aForrestVI & \aForrestVII & \aForrestVIII \tabularnewline
Forrest (child)  & \aForrestchildAll & \aForrestchildI & \aForrestchildII & \aForrestchildIII & \aForrestchildIV & \aForrestchildV & \aForrestchildVI & \aForrestchildVII & \aForrestchildVIII \tabularnewline
Forrest (v.o.)  & \aForrestvoAll & \aForrestvoI & \aForrestvoII & \aForrestvoIII & \aForrestvoIV & \aForrestvoV & \aForrestvoVI & \aForrestvoVII & \aForrestvoVIII \tabularnewline
Hancock  & \aHancockAll & \aHancockI & \aHancockII & \aHancockIII & \aHancockIV & \aHancockV & \aHancockVI & \aHancockVII & \aHancockVIII \tabularnewline
Jenny  & \aJennyAll & \aJennyI & \aJennyII & \aJennyIII & \aJennyIV & \aJennyV & \aJennyVI & \aJennyVII & \aJennyVIII \tabularnewline
Jenny (child)  & \aJennychildAll & \aJennychildI & \aJennychildII & \aJennychildIII & \aJennychildIV & \aJennychildV & \aJennychildVI & \aJennychildVII & \aJennychildVIII \tabularnewline
Lt. Dan  & \aLtdanAll & \aLtdanI & \aLtdanII & \aLtdanIII & \aLtdanIV & \aLtdanV & \aLtdanVI & \aLtdanVII & \aLtdanVIII \tabularnewline
Mrs. Gump  & \aMrsgumpAll & \aMrsgumpI & \aMrsgumpII & \aMrsgumpIII & \aMrsgumpIV & \aMrsgumpV & \aMrsgumpVI & \aMrsgumpVII & \aMrsgumpVIII \tabularnewline
Narrator  & \aNarratorAll & \aNarratorI & \aNarratorII & \aNarratorIII & \aNarratorIV & \aNarratorV & \aNarratorVI & \aNarratorVII & \aNarratorVIII \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

@@

@@

\section*{Dataset validation}
% Information about any validation carried out and/or any limitations of the
% datasets, including any allowances made for controlling bias or unwanted
% sources of variability.
% ~170 words => das wird beim folgenden Schreiben definitiv nichts werden
% Intro
In order to assess data quality, we investigated if contrasting speech-related events to non-speech related events lead to increased activation in areas known to be involved in semantic processing \citep{binder2009semantic, dewitt2012phoneme}.
Moreover, we tested if similar linguistic concepts providing high semantic information (proper nouns and nouns) contrasted to a concept providing low semantic information (conjunctions) lead to increased activation in congruent brain areas.
% Preprocessing
% die Daten aus Hanke2014 sind eigentlich nicht bewegungskorrigiert und aligned
% Quelle ist in vorliegendem Falle:
% juseless.inm7.de:/data/project/studyforrest/collection/phase1
% bei allem, was folgend mit alignment/co-registration zu tun hat, bin ich mir nicht sicher
We used fMRI BOLD data of the 2h audio-description (7 Tesla, 2s TR, partial
brain coverage with 1.4 mm isotropic voxels) \citep{hanke2014audiomovie} that
were already corrected for motion and aligned [wie?] to study specific group template [co-registered to MNI?].
All further steps analysis steps were carried out using Feat v6.00 (FMRI Expert
Analysis Tool)\citep{woolrich2001autocorr} as part of FSL v5.0.9 (FMRIB’s
Software Library)\citep{smith2004fsl}. Data were temporally high-pass filtered (cut-off 150s), spatially smoothed (Gaussian kernel; 4.0 mm FWHM), and the brain was extracted from surrounding tissue [keine Plan, ob die Reihenfolge so korrek ist]. A grand-mean intensity normalization of the entire 4D dataset was performed by a single multiplicative factor.
We implemented a standard three-level, voxel-wise general linear model (GLM) to average parameter estimates across the eight stimulus segments, and later across 19 subjects.
% 1st lvl
At the first level analysing each segment for each subject individually, we defined 26 regressors (s. table \ref{tab:regressors})
 based on information drawn from the annotation. The 20 most often occuring detailed tag labels (``nn'' with N=\rNnAll\space to ``prf'' with N=\rPrfAll) were modelled as such from the onset to offset of each word. The remaining tags were pooled to a single regressor (``tag\_other``; N=\rTagotherAll). The top 80 phonemes (``n'' with n=6053 to ``IY1'' with N=32) were pooled to the regressor ``phonemes'' (N=\rPhonesAll).
The ends of (complete) grammatical sentences were used as the onset of events, abitrarily lasting 0.2s, for the regressors ``sentence'' (N=\rSentenceAll).
A ``no-speech'' regressor (``no-sp''; N=\rNospAll) serving as a control condition was created by the following rationale: events were fitted into intervals between onsets and offsets of sentences/words assumed to contain no comprehensible speech. Each event of the no-speech condition had a minimum distance of 1.8s to onset/offsets of sentences/words and to each other onset of the no-speech condition (s. anno2events-files.py). A length of 0.07s was chosen for these events matching the average length of phonemes.
Two regressors reflecting auditory (low-level) features (left-right loudness/volume/amplitude difference; root mean squared amplitude) aligned to the frame rate of (40 ms) were modelled to reduce nuisance effects.
Hier (und das ggf auch mehr auf Korrelation der Regressoren eingehen. \ref{fig:reg-corr}).
Those 26 regressors were convolved with FSL's ``Double-Gamma HRF'' as a model of the hemodynamic response function. Temporal derivatives were also included in the design matrix, and it was subjected to the same temporal filtering as the BOLD time series. Finally, six motion parameters were used as additional nuisance regressors.
The following six t-contrasts were defined: 1) words (21 tag-related regressors) > no-speech; 2) no-speech > all 21 tag-related regressors; 3) proper nouns (``ne''; N=\rNeAll) > coordinate conjunctions (``kon''; N=\rKonAll); 4) coordinate conjunctions > proper nouns; 5) nouns (``nn'') > coordinate conjunctions, and 6) coordinate conjunctions > nouns. The first level analysis that fitted each voxel’s time course separately for each subject was performed in functional space preserving the orientation of the EPI images [richtig?].

>>>>

\begin{table*}[tbp]
\caption{Overview of the speech annotation's content for the whole stimulus and it's individual segments. The label ``Sentences''' comprises complete grammatical sentences (i.e. having a subject and a predicate, and additionally marked with a full stop in the annotation). The  ``Sentences'' also comprises exlamations or non-speech vocalizations in quick succession (e.g. ``ha, ha, ha'') or in isolation (e.g. ``ha'', at time points when speakers rapidly switch). The label ``Words'' comprises every single word or non-speech vocalization (N=\aPosNonspeechAll) in isolation.}
\label{tab:overview}
\begin{tabular}{llllllllll}
\toprule
\textbf{label} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8}\\
\midrule
sentences  & \aSentencesAll & \aSentencesI & \aSentencesII & \aSentencesIII & \aSentencesIV & \aSentencesV & \aSentencesVI & \aSentencesVII & \aSentencesVIII \tabularnewline
words  & \aWordsAll & \aWordsI & \aWordsII & \aWordsIII & \aWordsIV & \aWordsV & \aWordsVI & \aWordsVII & \aWordsVIII \tabularnewline
phonemes  & \aPhonesAll & \aPhonesI & \aPhonesII & \aPhonesIII & \aPhonesIV & \aPhonesV & \aPhonesVI & \aPhonesVII & \aPhonesVIII \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

% bei ein paar Namen bin ich ggf. von Labs abgewichen (genauer identifiziert, ggf. kleine Fehler korrigiert. Ist dann aber nur bei Personen, die 1-2x mit 1-2 Sätzen auftauchen.
\begin{table*}[btp]
\caption{Sentences spoken by the ten most often occurring speakers sorted alphabetically. The narrator only occurrs in the audio-description of the movie. Shown names are identical to the names used in \citep{labs2015portrayed}. Overall 97 persons were identified.}
\label{tab:speakers}
\begin{tabular}{llllllllll}
\toprule
\textbf{name} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8}\\
\midrule
Bubba  & \aBubbaAll & \aBubbaI & \aBubbaII & \aBubbaIII & \aBubbaIV & \aBubbaV & \aBubbaVI & \aBubbaVII & \aBubbaVIII \tabularnewline
Forrest  & \aForrestAll & \aForrestI & \aForrestII & \aForrestIII & \aForrestIV & \aForrestV & \aForrestVI & \aForrestVII & \aForrestVIII \tabularnewline
Forrest (child)  & \aForrestchildAll & \aForrestchildI & \aForrestchildII & \aForrestchildIII & \aForrestchildIV & \aForrestchildV & \aForrestchildVI & \aForrestchildVII & \aForrestchildVIII \tabularnewline
Forrest (v.o.)  & \aForrestvoAll & \aForrestvoI & \aForrestvoII & \aForrestvoIII & \aForrestvoIV & \aForrestvoV & \aForrestvoVI & \aForrestvoVII & \aForrestvoVIII \tabularnewline
Hancock  & \aHancockAll & \aHancockI & \aHancockII & \aHancockIII & \aHancockIV & \aHancockV & \aHancockVI & \aHancockVII & \aHancockVIII \tabularnewline
Jenny  & \aJennyAll & \aJennyI & \aJennyII & \aJennyIII & \aJennyIV & \aJennyV & \aJennyVI & \aJennyVII & \aJennyVIII \tabularnewline
Jenny (child)  & \aJennychildAll & \aJennychildI & \aJennychildII & \aJennychildIII & \aJennychildIV & \aJennychildV & \aJennychildVI & \aJennychildVII & \aJennychildVIII \tabularnewline
Lt. Dan  & \aLtdanAll & \aLtdanI & \aLtdanII & \aLtdanIII & \aLtdanIV & \aLtdanV & \aLtdanVI & \aLtdanVII & \aLtdanVIII \tabularnewline
Mrs. Gump  & \aMrsgumpAll & \aMrsgumpI & \aMrsgumpII & \aMrsgumpIII & \aMrsgumpIV & \aMrsgumpV & \aMrsgumpVI & \aMrsgumpVII & \aMrsgumpVIII \tabularnewline
Narrator  & \aNarratorAll & \aNarratorI & \aNarratorII & \aNarratorIII & \aNarratorIV & \aNarratorV & \aNarratorVI & \aNarratorVII & \aNarratorVIII \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

@@

\section*{Dataset validation}
% Information about any validation carried out and/or any limitations of the
% datasets, including any allowances made for controlling bias or unwanted
% sources of variability.
% ~170 words => das wird beim folgenden Schreiben definitiv nichts werden
% Intro
In order to assess data quality, we investigated if contrasting speech-related events to non-speech related events lead to increased activation in areas known to be involved in semantic processing \citep{binder2009semantic, dewitt2012phoneme}.
Moreover, we tested if similar linguistic concepts providing high semantic information (proper nouns and nouns) contrasted to a concept providing low semantic information (conjunctions) lead to increased activation in congruent brain areas.
% Preprocessing
% die Daten aus Hanke2014 sind eigentlich nicht bewegungskorrigiert und aligned
% Quelle ist in vorliegendem Falle:
% juseless.inm7.de:/data/project/studyforrest/collection/phase1
% bei allem, was folgend mit alignment/co-registration zu tun hat, bin ich mir nicht sicher
We used fMRI BOLD data of the 2h audio-description (7 Tesla, 2s TR, partial
brain coverage with 1.4 mm isotropic voxels) \citep{hanke2014audiomovie} that
were already corrected for motion and aligned [wie?] to study specific group template [co-registered to MNI?].
All further steps analysis steps were carried out using Feat v6.00 (FMRI Expert
Analysis Tool)\citep{woolrich2001autocorr} as part of FSL v5.0.9 (FMRIB’s
Software Library)\citep{smith2004fsl}. Data were temporally high-pass filtered (cut-off 150s), spatially smoothed (Gaussian kernel; 4.0 mm FWHM), and the brain was extracted from surrounding tissue [keine Plan, ob die Reihenfolge so korrek ist]. A grand-mean intensity normalization of the entire 4D dataset was performed by a single multiplicative factor.
We implemented a standard three-level, voxel-wise general linear model (GLM) to average parameter estimates across the eight stimulus segments, and later across 19 subjects.

@@

% 1st lvl
At the first level analysing each segment for each subject individually, we defined 26 regressors (s. table \ref{tab:regressors})
 based on information drawn from the annotation. The 20 most often occuring detailed tag labels (``nn'' with N=\rNnAll\space to ``prf'' with N=\rPrfAll) were modelled as such from the onset to offset of each word. The remaining tags were pooled to a single regressor (``tag\_other``; N=\rTagotherAll). The top 80 phonemes (``n'' with n=6053 to ``IY1'' with N=32) were pooled to the regressor ``phonemes'' (N=\rPhonesAll).
The ends of (complete) grammatical sentences were used as the onset of events, abitrarily lasting 0.2s, for the regressors ``sentence'' (N=\rSentenceAll).
A ``no-speech'' regressor (``no-sp''; N=\rNospAll) serving as a control condition was created by the following rationale: events were fitted into intervals between onsets and offsets of sentences/words assumed to contain no comprehensible speech. Each event of the no-speech condition had a minimum distance of 1.8s to onset/offsets of sentences/words and to each other onset of the no-speech condition (s. anno2events-files.py). A length of 0.07s was chosen for these events matching the average length of phonemes.
Two regressors reflecting auditory (low-level) features (left-right loudness/volume/amplitude difference; root mean squared amplitude) aligned to the frame rate of (40 ms) were modelled to reduce nuisance effects.
Hier (und das ggf auch mehr auf Korrelation der Regressoren eingehen. \ref{fig:reg-corr}).
Those 26 regressors were convolved with FSL's ``Double-Gamma HRF'' as a model of the hemodynamic response function. Temporal derivatives were also included in the design matrix, and it was subjected to the same temporal filtering as the BOLD time series. Finally, six motion parameters were used as additional nuisance regressors.
The following six t-contrasts were defined: 1) words (21 tag-related regressors) > no-speech; 2) no-speech > all 21 tag-related regressors; 3) proper nouns (``ne''; N=\rNeAll) > coordinate conjunctions (``kon''; N=\rKonAll); 4) coordinate conjunctions > proper nouns; 5) nouns (``nn'') > coordinate conjunctions, and 6) coordinate conjunctions > nouns. The first level analysis that fitted each voxel’s time course separately for each subject was performed in functional space preserving the orientation of the EPI images [richtig?].
